\documentclass[a4paper]{resume}

\begin{document}

%------------------------------------------------
% TITLE SECTION
%------------------------------------------------
\lastupdated{}
\namesection{Oscar L.}{Downing}{\href{mailto:odowning19@gmail.com}{odowning19@gmail.com} | \mynumber{}
	| \urlstyle{same}\url{www.linkedin.com/in/oscar-downing} | GitHub: \href{https://github.com/qozymandias}{\bf qozymandias}}

%------------------------------------------------
% LEFT COLUMN
%------------------------------------------------
\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
	%------------------------------------------------
	% Education
	%------------------------------------------------
	\section{Education}
	\smallsectionspace{}

	\subsection{University of New South Wales}
	\descript{B.E. (Hons) in Computer Engineering}
	\location{Feb. 2016 --- Aug. 2021 | Sydney, NSW}
	Honours thesis: ``Enhancements to the \href{https://github.com/NICTA/cogent}{\textsc{Cogent}} Property-Based
	Testing framework''. \\ Stephen Robjohns Memorial Rural Engineering Scholar.

	%------------------------------------------------
	% Skills
	%------------------------------------------------
	\section{Skills}
	\smallsectionspace{}

	\subsection{Programming}
	\smallsectionspace{}

	\location{Proficient}
	\rust{} \textbullet{} \clang{} \textbullet{} \cpp{} \textbullet{} \python{} \textbullet{} \bash{} \\
	\typescript{} \textbullet{} \javascript{} \\
	\smallsectionspace{}

	\location{Intermediate}
	\java{} \textbullet{} \kotlin{} \textbullet{} \haskell{} \textbullet{} \vhdl{} \\
	\verilog{} \textbullet{} \LaTeX{} \textbullet{} \isabelle{} \\
	\sectionspace{}

	\subsection{Web \& Cloud}
	\smallsectionspace{}
	\xml{} \textbullet{} \json{} \\
	\css{} \textbullet{} \react{} \\
	\aws{} \boto{} \textbullet{} \ectwo{} \textbullet{} \rds{} \\
	\jnciaJunos{} \textbullet{} \jnciaDevOps{} \\
	\sectionspace{}

	\subsection{Tools \& Frameworks}
	\smallsectionspace{}
	\mongo{} \textbullet{} \rocksdb{} \textbullet{} \cuda{} \\
	\linux{} \textbullet{} \git{} \textbullet{} \docker{} \\
	\cmake{} \textbullet{} \cargo{} \textbullet{} \conan{} \textbullet{} \gdb{} \\
	\pytest{} \textbullet{} \asyncio{} \textbullet{} \nodejs{} \\
	\spring{} \textbullet{} \googletest{} \textbullet{} \junit{} \\
	\cucumber{} \textbullet{} \ansible{} \\
	%  \\ \jenkins{} \\

	%------------------------------------------------
	% Side Projects & Volunteering
	%------------------------------------------------
	\section{Exp. Cont.}
	\smallsectionspace{}

	\runsubsection{Soprano Design}
	\descript{$|$ Graduate Software Engineer}
	\location{Aug. 2020 --- Dec. 2020}
	\textbullet{} Contributed to the development and QA of the MEMS platform, a \java{} web
	application (Apache Struts), tested with \junit{}/\cucumber{}. \\
	\smallsectionspace{}
	\smallsectionspace{}

	\runsubsection{Juniper Networks}
	\descript{$|$ Software Engineer Intern}
	\location{Feb. 2019 --- Aug. 2020}
	\textbullet{} Developed modules (\python{}/\ansible{}) for Network Implementation and Test Automation (\nita) tool.
	Configured/deployed \href{https://github.com/Juniper/warp17}{\warp} traffic gen tool for scale test. \\
	\textbullet{} Developed \href{https://github.com/Juniper/jsnapy}{JSnapy} scripts for automated testing. Upgraded
	static \junos{} config files into dynamic \jinja{}/\yaml{} files. \\
	\smallsectionspace{}

\end{minipage} % The end of the left column
\hfill
% do not delete this comment
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
	%------------------------------------------------
	% Experience
	%------------------------------------------------
	\section{Experience}
	\smallsectionspace{}

	\runsubsection{Delphinus Lab}
	\descript{$|$ Software Engineer}
	\location{Dec. 2023 --- Present}
	\vspace{\topsep}
	\begin{tightitemize}
		\item {
		            Contributed extensively to the design, development, and optimisation of the
		            \href{https://explorer.zkwasmhub.com}{zkWASM Playground}, a cloud-based platform for zero-knowledge proofs
		            of WebAssembly programs. Improved backend reliability, performance, and system observability
		            (\rust{}/\actix{}), and enhanced frontend integration (\react{}/\typescript{}).
		      }
		\item {
		            Designed and delivered key features including Proof Continuations, Task Archiving, integration of new
		            \href{https://github.com/DelphinusLab/zkWasm.git}{zkWASM} versions, and \rocksdb{} based Merkle storage.
		            Developed associated handlers, implemented robust cleanup routines, and enabled graceful shutdown and
		            recovery.
		      }
		\item {
		            Resolved critical \mongo{} performance and memory issues through query optimization, index strategy
		            redesign, client connection pooling, and efficient client resource management. Introduced request
		            throttling, dynamic fee scaling for large proofs, and structured log rotation support.
		      }
		\item {
		            Led major architectural refactors to core components such as the session update mechanism, dry-run
		            service, and auto-submit logic. Integrated cargo clippy across the codebase, eliminating unsafe patterns,
		            panics, and duplication, substantially improving maintainability and code health.
		      }
		\item {
		            Strengthened testing infrastructure and documentation, expanding and improving the end-to-end test framework and unit tests.
		            Added test coverage for edge cases (e.g., multi-prover synchronization, timeout handling), and authored
		            scripting utilities for testing and debugging.
		      }
		% \item {
		%             Improved developer and user experience, fixing UI validation bugs, reducing redundant REST calls, updating
		%             documentation, and enhancing startup routines and integration examples.
		%       }
	\end{tightitemize}
	\smallsectionspace{}

	\runsubsection{Dolby.io}
	\descript{$|$ Software Engineer}
	\location{Dec. 2021 --- Nov. 2023}
	\begin{tightitemize}
		\item {
		            Contributed to the Dolby Voice Conferencing Server (DVCS) project, a highly performant multi-threaded
		            audio mixing server written in \cpp{} (\cppstd{}/\conan{}/\cmake{}) for \voip{} communications; used by
		            the \dolbyio{} platform, designed for conferencing and virtual worlds communication at high-scale ---
		            thousands of real clients connected and talking. Designed/developed/tested critical new features (Dist
		            Attens).
		      }
		\item {
		            Developed supporting \python{}/\bash{} scripts for testing/CI/CD, including unit/system tests
		            (\googletest{}) and debugged complex multi-threaded problems in \cpp{} with \gdb{}. Improved \oats{}
		            end-to-end testing framework (\python{}/\asyncio{})
		            % which generated \rtp{} and impaired traffic for quality analysis.
		      }
		\item {
		            Improved CI scripts (as DVCS shifted its CI to \gitlab) and \aws{} scripts (\python/\boto) which saved
		            thousands of dollars in \ectwo{} computing costs. Additionally, built a \nodejs{} \typescript{}
		            application for viewing CI/CD pipelines which interfaced with \gitlab{} \rest{} APIs.
		      }
		\item {
		            Improved documentation for onboarding new engineers. Mentored interns, actively learned new technologies,
		            and presented talks internally.
		      }
		% \item {
		%             Wrote \vagrant{} VM scripts for developers (OS env setup with \bash{} scripting) and \docker{}
		%             scripts/images for testing/production.
		%       }
		\item {
		            Upgraded build/production environment to \debian{}, rewriting toolchains (\conan{}/\cmake{}) and fixing
		            bugs uncovered by the new compiler; including rewriting packaging scripts and supporting \python scripts.
		      }
		% \item {
		%             Built client-side and server-side applications (\nodejs{} \typescript{}/ \javascript{}) utilising
		%             customer-facing APIs for internal competitions.
		%       }
	\end{tightitemize}
	\smallsectionspace{}

	\runsubsection{Atlassian}
	\descript{$|$ Site Reliability Engineer Intern}
	\location{Nov. 2020 --- Feb. 2021}
	\begin{tightitemize}
		\item {
		            Worked with Shard Capacity Management team on the Tenant Placement Service project: an internal \aws{}
		            automation microservice, being developed to manage the \rds{} fleet (which hosts data from \jira{} and
		            \conf{} cloud products).
		      }
		\item {
		            Designed/developed automation of manual tasks relating to \rds{} life-cycle management. Creating
		            new/deleting \rds{} instances and auto-scaling low storage \rds{}. Implemented tracking and
		            reporting for internal audits of \rds{} events. \kotlin{}/\spring{}, with a \postgres{} DB (using
		            \jpa{}) and \rest{} APIs; Used in prod, saving the team manual effort and impacting $\num{150000} +$
		            customers.
		      }
	\end{tightitemize}
	\smallsectionspace{}

\end{minipage}
\end{document}
